Sustainable Indicators

### 2020-11-29 01-Sustainable-indicators.Rmd
adding the research axis
adding LCA and 3D printing

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
#bibliography: Biblio.bib
#nocite: '@*'
---

@@

>>>>

---
title: "Sustainable Indicators"
description: |
  Some additional details about the website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
repository_url: https://github.com/LF2L/everest-bio
bibliography: 01-Sustainable-indicators.bib
nocite: '@*'
---

@@

# Rationale

## LCA and 3D Printing

- AM’s environmental performance is seldom investigated [@Saade2020].
